Dependent Object Types

### 2012-08-30 doc/candidacy/macros.tex
compact code

% \lstset{basicstyle=\footnotesize\ttfamily, breaklines=true, language=scala, tabsize=2, columns=fixed, mathescape=false,includerangemarker=false}
% thank you, Burak 
% (lstset tweaking stolen from
% http://lampsvn.epfl.ch/svn-repos/scala/scala/branches/typestate/docs/tstate-report/datasway.tex)
\lstset{
    xleftmargin=1em,%
    framesep=5pt,%
    frame=none,%
    captionpos=b,%
    fontadjust=true,%
    columns=[c]fixed,%
    keepspaces=false,%
    basewidth={0.56em, 0.52em},%
    tabsize=2,%
    basicstyle=\footnotesize\tt,% \small\tt
    commentstyle=\textit,%
    keywordstyle=\bfseries,%
    escapechar=\%,%
}

>>>>

% \lstset{basicstyle=\footnotesize\ttfamily, breaklines=true, language=scala, tabsize=2, columns=fixed, mathescape=false,includerangemarker=false}
% thank you, Burak 
% (lstset tweaking stolen from
% http://lampsvn.epfl.ch/svn-repos/scala/scala/branches/typestate/docs/tstate-report/datasway.tex)
\lstset{
    xleftmargin=1em,%
    framesep=5pt,%
    frame=none,%
    captionpos=b,%
    fontadjust=true,%
    columns=[c]fixed,%
    keepspaces=false,%
    basewidth={0.56em, 0.52em},%
    tabsize=2,%
    basicstyle=\scriptsize\tt,% \small\tt
    commentstyle=\textit,%
    keywordstyle=\bfseries,%
    escapechar=\%,%
}

### 2012-08-30 doc/candidacy/report.tex
implement lib for tribe ex. give up on emulating out.
out works now
compact code

Now, we can emulate this Tribe example in Scala at the expense of some
synctactic overhead, since further binding and ``out'' selection are
not native.
\lstinputlisting{tribe.scala}

>>>>

Now, we can emulate this Tribe example in Scala at the expense of some
synctactic overhead, since further binding and ``out'' selection are
not native. Emulating ``out'' faithfully involves a bit of hackery in
making Scala recognize that, for example, \code{e.from.type} is a
subtype of \code{e.out.Node}. As noted in the paper, using ``out'' in
library code obscures the symmetry between the parameters (for
example, in the \code{distance} method below) but allows the family
object to be recovered without being explicitly passed around
(contrast with the method \code{distance2}).
\lstinputlisting{tribe.scala}
